Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2014-10-25 tex/scam/sparsistency.tex
acdc population, new prop for alt form
minor fix

We divide our analysis into two parts. We first establish a sufficient
deterministic condition for consistency of the sparsity pattern
selection procedure---a property sometimes called \textit{sparsistency}.
We then consider the
stochastic setting and argue that the deterministic conditions hold
with high probability. Note that in all of our results and analysis, we let $c,
C$ represent absolute constants; the actual values of $c,C$ may change from line to line.

@@

\end{corollary}
The above corollary implies that sparsistency is achievable at the
same exponential scaling of the ambient dimension scaling attained
with parametric models, $p = O(\exp(n^c))$ for $c<1$.  The cost of
nonparametric modeling through shape constraints 
is reflected in the scaling with respect to
the number of relevant variables, which can scale as $s = o(n^{4/25})$.

>>>>

%Our goal is to show that, as $n \rightarrow \infty$ and $p$ scales as $exp(-n^c)$, we have that the set of variables outputted by  $\hat{S}$

We divide our analysis into two parts. We first establish a sufficient
deterministic condition for consistency of the sparsity pattern
screening procedure.  We then consider the
stochastic setting and argue that the deterministic conditions hold
with high probability. Note that in all of our results and analysis, we let $c,
C$ represent absolute constants; the actual values of $c,C$ may change from line to line.

@@

\end{corollary}
The above corollary implies that consistent variable selection is
achievable at the same exponential scaling of the ambient dimension
scaling attained with parametric models, $p = O(\exp(n^c))$ for $c<1$.
The cost of nonparametric modeling through shape constraints is
reflected in the scaling with respect to the number of relevant
variables, which can scale as $s = o(n^{4/25})$.
